Historical supply of timber harvest residues in west-central Alberta

### 2021-09-10 analysis/manuscript.Rmd
sept 10

---
title: "Historical supply of timber harvest residues in west-central Alberta"
author:

- Glen W Armstrong^[Department of Renewable Resources, University of Alberta]
- Jay Anderson^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
- Alex McPhee^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
date: "13/07/2021"
output:
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
  word_document:
  html_document:
    df_print: paged
bibliography: historicalResidueSupply.bib
---

@@

Using @aWholeBunchOfMagic, the truck rate was set to 
\$`r truck_rate`/odmt/h.

>>>>

---
title: "Historical supply of timber harvest residues in west-central Alberta"
author:
- Glen W Armstrong^[Department of Renewable Resources, University of Alberta]
- Jay Anderson^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
- Alex McPhee^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
date: "2021-09-10"
output:
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
  word_document:
  html_document:
    df_print: paged
bibliography: historicalResidueSupply.bib
---

@@

Using *blah blah blah* , the truck rate was set to 
\$`r truck_rate`/odmt/h.
